---
title: "German climate tracker"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    social: menu
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(lubridate)
library(tidyverse)
library(rdwd)
library(plotly)
library(shiny)
library(leaflet)
library(htmltools)
library(readr)

Sys.setlocale(locale = "English")
```

# Averages and trends

```{r}
Liste <-
  c(
    "Berlin-Tempelhof",
    "Erfurt-Weimar",
    "Jena (Sternwarte)",
    "Frankfurt/Main",
    "Stuttgart-Echterdingen",
    "Hannover",
    "Hamburg-Neuwiedenthal",
    "Koeln-Bonn",
    "Potsdam",
    "Duesseldorf",
    "Dresden-Hosterwitz",
    "Muenchen-Flughafen",
    "Eschwege",
    "Norderney",
    "List auf Sylt",
    "Schmuecke",
    "Brocken",
    "Fichtelberg",
    "Feldberg/Schwarzwald",
    "Zugspitze",
    "Saarbruecken-Ensheim",
    "Leipzig/Halle",
    "Mainz-Lerchenberg (ZDF)",
    "Bremen",
    "Kiel-Holtenau",
    "Rostock-Warnemuende",
    "Magdeburg",
    "Schwerin",
    "Grosser Arber",
    "Nuernberg",
    "Friedrichshafen",
    "Cottbus",
    "Kleiner Feldberg/Taunus",
    "Muenster/Osnabrueck",
    "Fulda-Horas",
    "Waren (Mueritz)",
    "Eisenach",
    "Kleiner Inselsberg",
    "Gera-Leumnitz",
    "Goettingen",
    "Wuerzburg",
    "Aachen-Orsbach",
    "Wittenberg",
    "Muehlhausen/Thueringen-Goermar",
    "Freiburg",
    "Ingolstadt (Flugplatz)",
    "Regensburg",
    "Chemnitz",
    "Trier-Petrisberg",
    "Tann/Rhoen",
    "Teterow",
    "Nossen",
    "Freiburg/Elbe",
    "Lenzen/Elbe",
    "Luebeck-Blankensee",
    "Fehmarn",
    "Bremerhaven",
    "Braunschweig",
    "Chieming",
    "Augsburg",
    "Neuhaus am Rennweg",
    "Heinersreuth-Vollhof",
    "Helgoland"
  )%>%
  sort()
```

```{r eval=F}

#Um den Datensatz herunterzuladen beim ersten Ausführen eval=T setzen

dataset <- map(Liste, function(x)
    bind_rows(
  readDWD(dataDWD(
    selectDWD(x, res = "daily", var = "kl", per = "historical"), read = FALSE
  ), varnames = TRUE) ,
  readDWD(dataDWD(
    selectDWD(x, res = "daily", var = "kl", per = "recent"), read = FALSE
  ), varnames = TRUE) %>%
    filter(MESS_DATUM>=dmy("01.01.2020")#&MESS_DATUM<=dmy("31.12.2020")
           )
  ) %>%
    mutate(
      Name_Station = x,
      Jahr = MESS_DATUM %>% year(),
      Monat = MESS_DATUM %>% month(label = T, abbr = F)
    )) %>% bind_rows()

saveRDS(dataset,"data_Klima.RDS")
```

```{r}
dataset<-readRDS(file ="data_Klima.RDS" )%>%
  filter(MESS_DATUM<=ymd("2020-12-31"))%>%
    mutate(
      Monat = MESS_DATUM %>% month(.,label = T, abbr = F),
      Year=Jahr
    )

month_list <- c("Entire Year", format(ISOdate(2021, 1:12, 1), "%B"))

Liste_Bundeslaender<-c("Bayern"
                  , "Baden-Wuerttemberg", "Rheinland-Pfalz", "Hessen", "Niedersachsen"
                  , "Schleswig-Holstein", "Saarland", "Hamburg", "Thueringen"
                  , "Nordrhein-Westfalen", "Sachsen", "Brandenburg", "Sachsen-Anhalt"
                  , "Mecklenburg-Vorpommern", "Bremen", "Berlin")

data(metaIndex)

Index_Wetterstationen<-metaIndex
```

## Column {.sidebar}

```{r}
selectInput('Station', HTML(paste("<b>","Station name","</b>")), Liste, selected = "Erfurt-Weimar")

selectInput(
  'ycol',
  HTML(paste("<b>","Variable","</b>")),
  c(
    "Temperature",
    "Snow_height",
    "Sunshine_duration",
    "Precipitation_height"
  ),
  selected = names(dataset)[[1]]
)

selectInput(
  'month',
  HTML(paste("<b>","Year / Month","</b>")),
  c(
    month_list
  ),
  selected = "Entire Year"
)

radioButtons("regline",
             HTML(paste("<b>Trend line:</b>", "(Regression line)", sep="<br/>")),
             c("Yes" = TRUE,
               "No" = FALSE),
             selected = FALSE)
```

<b>Location:</b>

```{r}
renderLeaflet({
Index_Wetterstationen%>%filter(Stationsname==input$Station)%>%
  distinct(Stationsname,.keep_all = T)%>%
  leaflet()%>%
  addTiles()%>%
  addMarkers(
    ~geoLaenge,
    ~geoBreite,
    popup = ~Stationsname,
    label = ~str_c(
        "<p>",
        "<b>",
        Stationsname,
        "</b>",
        " <p> ",
        "State: ",
        Bundesland,
        " <p> ",
        "Station height: ",
        Stationshoehe,
        " m",
        " <p> ",
        "Station_id: ",
        Stations_id,
        "</p>"
      )%>%
      HTML()
  )
})
```

## Column {data-width="1000"}

### Average `r reactive({input$month})`

```{r}
selectedData <- reactive({
  dataset %>%
    {
      if (input$month != "Entire Year")
        filter(., Monat == input$month)
      else
        (.)
    }  %>%
    group_by(Year, Name_Station) %>%
    summarise(
      "Temperature" = mean(TMK.Lufttemperatur) %>% round(2),
      "Snow_height" = mean(SHK_TAG.Schneehoehe) %>% round(2),
      "Sunshine_duration" = mean(SDK.Sonnenscheindauer) %>% round(2),
      "Precipitation_height" = mean(RSK.Niederschlagshoehe) %>% round(2)
    ) %>% filter(Name_Station == input$Station)
})


renderPlotly({
  p1 <-
    ggplot(data = selectedData(),
           aes_string(
             x = "Year",
             y = input$ycol,
             fill = input$ycol)
             ) +
    geom_bar(stat = "identity", size = 10) +
    scale_fill_gradient(
      low = case_when(
        input$ycol == "Temperature" ~ "blue",
        input$ycol == "Snow_height" ~ "green",
        input$ycol == "Sunshine_duration" ~ "black",
        input$ycol == "Precipitation_height" ~ "brown"
      ),
      high = case_when(
        input$ycol == "Temperature" ~ "red",
        input$ycol == "Snow_height" ~ "blue",
        input$ycol == "Sunshine_duration" ~ "yellow",
        input$ycol == "Precipitation_height" ~ "blue"
      )
    ) +
    xlab("Year") +
    theme(legend.position = "none")
  
  ggplotly(if (input$regline) {
    print(p1 + geom_smooth(method = 'lm', se = F))
  }
  else{
    p1
  },tooltip = c("x","y"))
})
```

# How was the weather when and where? 

## Column {.sidebar}

```{r}
selectInput('Station2', HTML(paste("<b>","Station name","</b>")), Liste, selected = "Erfurt-Weimar")

dateInput("date1",HTML(paste("<b>","Date","</b>")), value = "2020-12-31", max="2020-12-31", startview="decade")
```

## Column {data-width="300"}

```{r}
selectedData2<-
  reactive({
  dataset%>%filter(MESS_DATUM==input$date1)%>%
    filter(Name_Station==input$Station2)
})

renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Average temperature\n","on ", input$date1%>%format("%d.%m.%Y")))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label = 
           if((nrow(selectedData2())[1] == 0)){"Not\navailable"}
           else if ( is.na(selectedData2()$TMK.Lufttemperatur)) {"Not\navailable"}
           else (paste0(selectedData2()$TMK.Lufttemperatur%>%round(1),"°C")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Minimum temperature\n","on ", input$date1%>%format("%d.%m.%Y")))+ 
  annotate("text", x = 0.5, y = 0.4,
           label = 
           if((nrow(selectedData2())[1] == 0)){"Not\navailable"}
           else if ( is.na(selectedData2()$TNK.Lufttemperatur_Min)) {"Not\navailable"}
           else (paste0(selectedData2()$TNK.Lufttemperatur_Min%>%round(1),"°C")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Maximum temperature\n","on ", input$date1%>%format("%d.%m.%Y")))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label = 
           if((nrow(selectedData2())[1] == 0)){"Not\navailable"}
           else if ( is.na(selectedData2()$TXK.Lufttemperatur_Max)) {"Not\navailable"}
           else (paste0(selectedData2()$TXK.Lufttemperatur_Max%>%round(1),"°C")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

## Column {data-width="300"}

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Sunshine duration\n","on ", input$date1%>%format("%d.%m.%Y")))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label = 
           if((nrow(selectedData2())[1] == 0)){"Not\navailable"}
           else if ( is.na(selectedData2()$SDK.Sonnenscheindauer)) {"Not\navailable"}
           else (paste0(selectedData2()$SDK.Sonnenscheindauer%>%round(1)," hours")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Precipitation height\n","on ", input$date1%>%format("%d.%m.%Y")))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label = 
           if((nrow(selectedData2())[1] == 0)){"Not\navailable"}
           else if ( is.na(selectedData2()$RSK.Niederschlagshoehe)) {"Not\navailable"}
           else (paste0(selectedData2()$RSK.Niederschlagshoehe%>%round(1)," cm")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Snow height\n","on ", input$date1%>%format("%d.%m.%Y")))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label = 
           if((nrow(selectedData2())[1] == 0)){"Not\navailable"}
           else if ( is.na(selectedData2()$SHK_TAG.Schneehoehe)) {"Not\navailable"}
           else (paste0(selectedData2()$SHK_TAG.Schneehoehe%>%round(1)," cm")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

## Column {data-width="300"}

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Wind speed (daily average)\n","on ", input$date1%>%format("%d.%m.%Y")))+ 
  annotate("text",
           x = 0.5, 
           y = 0.4,
           label =
           if((nrow(selectedData2())[1] == 0)){"Not\navailable"}
           else if ( is.na(selectedData2()$FM.Windgeschwindigkeit)) {"Not\navailable"}
           else (paste0(selectedData2()$FM.Windgeschwindigkeit%>%round(1)," m/sec")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Wind peak\n","on ", input$date1%>%format("%d.%m.%Y")))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label = 
           if((nrow(selectedData2())[1] == 0)){"Not\navailable"}
           else if ( is.na(selectedData2()$FX.Windspitze)) {"Not\navailable"}
           else (paste0(selectedData2()$FX.Windspitze%>%round(1)," m/sec")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Air pressure (daily average)\n","on ", input$date1%>%format("%d.%m.%Y")))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label =
           if((nrow(selectedData2())[1] == 0)){"Not\navailable"}
           else if ( is.na(selectedData2()$PM.Luftdruck)) {"Not\navailable"}
           else (paste0(selectedData2()$PM.Luftdruck," hpa")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text(size=25))
})
```

# Year-to-year comparison

## Column {.sidebar}

```{r}
selectInput('Station4', HTML(paste("<b>","Station name","</b>")), Liste, selected = "Erfurt-Weimar")

selectInput(
  'ycol3',
  HTML(paste("<b>","Variable","</b>")),
  c(
    "Temperature",
    "Snow_height",
    "Sunshine_duration",
    "Precipitation_height"
  ),
  selected = names(dataset)[[1]]
)

selectInput(
  'month2',
  HTML(paste("<b>","Year / Month","</b>")),
  c(
    month_list
  ),
  selected = "Entire Year"
)

selectInput(
  'type',
  HTML(paste("<b>","Plot type","</b>")),
  c(
    c("Line plot","Scatter plot","Bar plot")
  ),
  selected = "Line plot"
)

radioButtons("smooth_trend",
             HTML(paste("<b>Trend line over all selected years:</b>", "(smooth)", sep="<br/>")),
             c("Yes" = TRUE,
               "No" = FALSE),
             selected = FALSE)

textInput("text", HTML(paste("<b>","Years","</b>")), value = "2020,2019")
```

Multiple years can be compared in this field. Simply enter as many years as desired. The years must be separated by a comma and must not contain a space.

Example:

2020,2019,1999,1980

## Column {data-width="1000"}

### Annual trends

```{r}
selectedData3 <- reactive({
  dataset %>%
    rename("Temperature"=TMK.Lufttemperatur,
           "Snow_height"=SHK_TAG.Schneehoehe,
           "Sunshine_duration"=SDK.Sonnenscheindauer,
           "Precipitation_height"=RSK.Niederschlagshoehe)%>%
    {
      if (input$month2 != "Entire Year")
        filter(., Monat == input$month2)
      else
        (.)
    }%>%
    filter(.,Year %in% strsplit(input$text, ",")[[1]])%>%
    filter(Name_Station==input$Station4)%>%
  mutate(year = factor(year(MESS_DATUM)),
         Date = update(MESS_DATUM, year = 1)%>%as.Date())
})

renderPlotly({

p2<-ggplot(data = selectedData3(),
           aes_string(
             x = "Date",
             y = input$ycol3 )) +
      {if(input$type=="Line plot")
      {geom_line(aes_string(color=selectedData3()$year))}
    else if(input$type=="Scatter plot")
    {geom_point(aes_string(color=selectedData3()$year))}
    else if(input$type=="Bar plot")
    {geom_col(aes_string(fill=selectedData3()$year), alpha=0.3, position = 'identity')}
    }+
  scale_x_date(date_breaks = "1 week", date_labels = "%d-%b")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))+
    labs(x="",color = "Years")

  ggplotly(if (input$smooth_trend) {
    print(p2 + geom_smooth())
  }
  else{
    p2
  },tooltip = c("x","y"))
})
```

# Climate records

## Column {.sidebar}

```{r}
selectInput('Station3', HTML(paste("<b>","Station name","</b>")), c("All stations",Liste), selected = "All stations")

radioButtons("record",
             HTML(paste("<b>","Maximum / Minumum","</b>")),
             c("Maximum" = "Maximum",
               "Minimum" = "Minimum"),
             selected = "Maximum")
```

## Column {data-width="300"}

```{r}
selectedData4<-
  reactive({
  dataset%>%
      {if (input$Station3 != "All stations")
    filter(.,Name_Station==input$Station3)
        else(.)
      }
})
```

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Average temperature"))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label = 
           if((nrow(selectedData4())[1] == 0)){"Not\navailable"}
           else if(input$record=="Maximum")
             paste0(
             selectedData4()$TMK.Lufttemperatur%>%
               max(na.rm = T)%>%round(1),"°C","\n",selectedData4()[which.max(selectedData4()$TMK.Lufttemperatur),]$Name_Station,"\n","on ",selectedData4()[which.max(selectedData4()$TMK.Lufttemperatur),]$MESS_DATUM%>%format("%d.%m.%Y"))
           else if(input$record=="Minimum")
             paste0(
             selectedData4()$TMK.Lufttemperatur%>%
               min(na.rm = T)%>%round(1),"°C","\n",selectedData4()[which.min(selectedData4()$TMK.Lufttemperatur),]$Name_Station,"\n","on ",selectedData4()[which.min(selectedData4()$TMK.Lufttemperatur),]$MESS_DATUM%>%format("%d.%m.%Y"))
             ,
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Minimum temperature"))+ 
  annotate("text", x = 0.5, y = 0.4,
           label = 
           if((nrow(selectedData4())[1] == 0)){"Not\navailable"}
        else if(input$record=="Maximum")
             paste0(
             selectedData4()$TNK.Lufttemperatur_Min%>%
               max(na.rm = T)%>%round(1),"°C","\n",selectedData4()[which.max(selectedData4()$TNK.Lufttemperatur_Min),]$Name_Station,"\n","on ",selectedData4()[which.max(selectedData4()$TNK.Lufttemperatur_Min),]$MESS_DATUM%>%format("%d.%m.%Y"))
           else if(input$record=="Minimum")
             paste0(
             selectedData4()$TNK.Lufttemperatur_Min%>%
               min(na.rm = T)%>%round(1),"°C","\n",selectedData4()[which.min(selectedData4()$TNK.Lufttemperatur_Min),]$Name_Station,"\n","on ",selectedData4()[which.min(selectedData4()$TNK.Lufttemperatur_Min),]$MESS_DATUM%>%format("%d.%m.%Y")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Maximum temperature"))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label = 
           if((nrow(selectedData4())[1] == 0)){"Not\navailable"}
           else if(input$record=="Maximum")
             paste0(
             selectedData4()$TXK.Lufttemperatur_Max%>%
               max(na.rm = T)%>%round(1),"°C","\n",selectedData4()[which.max(selectedData4()$TXK.Lufttemperatur_Max),]$Name_Station,"\n","on ",selectedData4()[which.max(selectedData4()$TXK.Lufttemperatur_Max),]$MESS_DATUM%>%format("%d.%m.%Y"))
           else if(input$record=="Minimum")
             paste0(
             selectedData4()$TXK.Lufttemperatur_Max%>%
               min(na.rm = T)%>%round(1),"°C","\n",selectedData4()[which.min(selectedData4()$TXK.Lufttemperatur_Max),]$Name_Station,"\n","on ",selectedData4()[which.min(selectedData4()$TXK.Lufttemperatur_Max),]$MESS_DATUM%>%format("%d.%m.%Y")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

## Column {data-width="300"}

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Sunshine duration"))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label = 
           if((nrow(selectedData4())[1] == 0)){"Not\navailable"}
           else if(input$record=="Maximum")
             paste0(
             selectedData4()$SDK.Sonnenscheindauer%>%
               max(na.rm = T)%>%round(1)," hours","\n",selectedData4()[which.max(selectedData4()$SDK.Sonnenscheindauer),]$Name_Station,"\n","on ",selectedData4()[which.max(selectedData4()$SDK.Sonnenscheindauer),]$MESS_DATUM%>%format("%d.%m.%Y"))
           else if(input$record=="Minimum")
             paste0(
             selectedData4()$SDK.Sonnenscheindauer%>%
               min(na.rm = T)%>%round(1)," hours","\n",selectedData4()[which.min(selectedData4()$SDK.Sonnenscheindauer),]$Name_Station,"\n","on ",selectedData4()[which.min(selectedData4()$SDK.Sonnenscheindauer),]$MESS_DATUM%>%format("%d.%m.%Y")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Precipitation height"))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label = 
           if((nrow(selectedData4())[1] == 0)){"Not\navailable"}
           else if(input$record=="Maximum")
             paste0(
             selectedData4()$RSK.Niederschlagshoehe%>%
               max(na.rm = T)%>%round(1)," cm","\n",selectedData4()[which.max(selectedData4()$RSK.Niederschlagshoehe),]$Name_Station,"\n","on ",selectedData4()[which.max(selectedData4()$RSK.Niederschlagshoehe),]$MESS_DATUM%>%format("%d.%m.%Y"))
           else if(input$record=="Minimum")
             paste0(
             selectedData4()$RSK.Niederschlagshoehe%>%
               min(na.rm = T)%>%round(1)," cm","\n",selectedData4()[which.min(selectedData4()$RSK.Niederschlagshoehe),]$Name_Station,"\n","on ",selectedData4()[which.min(selectedData4()$RSK.Niederschlagshoehe),]$MESS_DATUM%>%format("%d.%m.%Y")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Snow height"))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label = 
           if((nrow(selectedData4())[1] == 0)){"Not\navailable"}
           else if(input$record=="Maximum")
             paste0(
             selectedData4()$SHK_TAG.Schneehoehe%>%
               max(na.rm = T)%>%round(1)," cm","\n",selectedData4()[which.max(selectedData4()$SHK_TAG.Schneehoehe),]$Name_Station,"\n","on ",selectedData4()[which.max(selectedData4()$SHK_TAG.Schneehoehe),]$MESS_DATUM%>%format("%d.%m.%Y"))
           else if(input$record=="Minimum")
             paste0(
             selectedData4()$SHK_TAG.Schneehoehe%>%
               min(na.rm = T)%>%round(1)," cm","\n",selectedData4()[which.min(selectedData4()$SHK_TAG.Schneehoehe),]$Name_Station,"\n","on ",selectedData4()[which.min(selectedData4()$SHK_TAG.Schneehoehe),]$MESS_DATUM%>%format("%d.%m.%Y")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

## Column {data-width="300"}

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Wind speed"))+ 
  annotate("text",
           x = 0.5, 
           y = 0.4,
           label =
           if((nrow(selectedData4())[1] == 0)){"Not\navailable"}
           else if(input$record=="Maximum")
             paste0(
             selectedData4()$FM.Windgeschwindigkeit%>%
               max(na.rm = T)%>%round(1)," m/sec","\n",selectedData4()[which.max(selectedData4()$FM.Windgeschwindigkeit),]$Name_Station,"\n","on ",selectedData4()[which.max(selectedData4()$FM.Windgeschwindigkeit),]$MESS_DATUM%>%format("%d.%m.%Y"))
           else if(input$record=="Minimum")
             paste0(
             selectedData4()$FM.Windgeschwindigkeit%>%
               min(na.rm = T)%>%round(1)," m/sec","\n",selectedData4()[which.min(selectedData4()$FM.Windgeschwindigkeit),]$Name_Station,"\n","on ",selectedData4()[which.min(selectedData4()$FM.Windgeschwindigkeit),]$MESS_DATUM%>%format("%d.%m.%Y")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Wind peak"))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label = 
           if((nrow(selectedData4())[1] == 0)){"Not\navailable"}
           else if(input$record=="Maximum")
             paste0(
             selectedData4()$FX.Windspitze%>%
               max(na.rm = T)%>%round(1)," m/sec","\n",selectedData4()[which.max(selectedData4()$FX.Windspitze),]$Name_Station,"\n","on ",selectedData4()[which.max(selectedData4()$FX.Windspitze),]$MESS_DATUM%>%format("%d.%m.%Y"))
           else if(input$record=="Minimum")
             paste0(
             selectedData4()$FX.Windspitze%>%
               min(na.rm = T)%>%round(1)," m/sec","\n",selectedData4()[which.min(selectedData4()$FX.Windspitze),]$Name_Station,"\n","on ",selectedData4()[which.min(selectedData4()$FX.Windspitze),]$MESS_DATUM%>%format("%d.%m.%Y")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text( size=25))
})
```

```{r}
renderPlot({
ggplot(data.frame(x=runif(10),y=runif(10)), aes(x=x, y=y))+
  labs(title=paste0("Air pressure (daily average)"))+ 
  annotate("text",
           x = 0.5,
           y = 0.4,
           label =
           if((nrow(selectedData4())[1] == 0)){"Not\navailable"}
           else if(input$record=="Maximum")
             paste0(
             selectedData4()$PM.Luftdruck%>%
               max(na.rm = T)%>%round(1)," hpa","\n",selectedData4()[which.max(selectedData4()$PM.Luftdruck),]$Name_Station,"\n","on ",selectedData4()[which.max(selectedData4()$PM.Luftdruck),]$MESS_DATUM%>%format("%d.%m.%Y"))
           else if(input$record=="Minimum")
             paste0(
             selectedData4()$PM.Luftdruck%>%
               min(na.rm = T)%>%round(1)," hpa","\n",selectedData4()[which.min(selectedData4()$PM.Luftdruck),]$Name_Station,"\n","on ",selectedData4()[which.min(selectedData4()$PM.Luftdruck),]$MESS_DATUM%>%format("%d.%m.%Y")),
           size=20)+ 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),
        axis.text.y=element_blank(),axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),legend.position="none")+ 
  theme(plot.title = element_text(size=25))
})
```

# Weather stations overview

```{r}
Index_Wetterstationen%>%
  tibble()%>%
  filter(res=="daily")%>%
  distinct(Stationsname, .keep_all = TRUE)%>%
  filter(Stationsname %in% Liste)%>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(
    ~ geoLaenge,
    ~ geoBreite,
    popup = ~ as.character(Stationsname),
    label = ~ lapply(
      str_c(
        "<p>",
        "<b>",
        Stationsname,
        "</b>",
        " <p> ",
        "State: ",
        Bundesland,
        " <p> ",
        "Statio height: ",
        Stationshoehe,
        " m",
        " <p> ",
        "Station ID: ",
        Stations_id,
        "</p>"
      ),
      htmltools::HTML
    )
  )
```

# About

## Column {.sidebar}

This web app is developed and maintained by  Tobias Kellner (<https://github.com/TobiasKellner>).\
This dashboard is used to prepare and interactively visualize historical climate data from the German Weather Service.\
For `r length(Liste)` weather stations the historical data can be visualized.\
In principle, it is possible to include additional weather stations.\
However, the data must be checked manually beforehand.\
Just send me an email, if you want to add more weather stations:
[tobias.kellner\@uni-erfurt.de](tobias.kellner@uni-erfurt.de)\
Praise, criticism and suggestions for improvement are also welcome.

The data was downloaded using the R package [rdwd](https://cran.r-project.org/web/packages/rdwd/index.html).\
The source code of this web app is public and can be viewed after clicking on the upper right icon. Gaps in the graphs are due to missing values in the time series of the German Weather Service.
